Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
more updates

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
 12.7\%\comments{(33 misses)} of the \numFaults{} cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
the diagnostic accuracy by \avgImprov\ in 51\% of the cases. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
	 Total      & 207  & 78.4\% & 217 & 83.0\%
	 				& 227 & 83.8\% & 237 & 88.2\% & 260 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table*}

@@

We observed that $33$ of the $260$ faulty versions do not include the
faulty statements in the slicer report after slicing.
As observed in~\ref{table:fsws}, \combpar{k}
finds the faulty statements faster than \sfl{}$^{k}$.

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to evaluate the effects of combining \ds{} with \sfl{}. We suspect
that several highly suspicious components---often involved in failing,
but seldom in passing test runs---may be unrelated to the bug. With
the aforementioned combination, such components could be located and
their suspiciousness reduced.  This study also discusses the practical
impact of the \ds{} key limitation---the risk of missing faulty
statements. Results indicate that \ds{} misses faulty statements in
 9\%\comments{(23 misses)} of the \numFaults{} cases and that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves on average
the diagnostic accuracy by \avgImprov\ in 51\% of the cases. To sum,
we found that the \ds{}-\sfl{} combination was practical and effective
and encourage new \sfl{} techniques to be evaluated against that
optimization.
\end{abstract}

@@

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
	 Total      & 207  & 79.6\% & 217 & 83.5\%
	 				& 227 & 87.3\% & 237 & 91.2\% & 260 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table*}

@@

In~\ref{table:fsws}, we observe that

\combpar{k}
finds the faulty statements faster than \sfl{}$^{k}$. For both $k$ scenarios ($k=5$ or $k=10$), \combpar{k} performs better, i.e., it misses less faulty statements than \sfl{}$^{k}$.

\combpar{k}The best scena $23$ of the $260$ ($8.8\%$) faults do not include the
faulty statements in the slicer report after slicing the $10$ highest faulty classes.
